The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-03-11 manuscript/manuscript.tex
Updates after John's visiting.

\title{Cosmic evolution of the mass relation between supermassive black holes and their host galaxies up to $z\sim1.7$}

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{2}, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{2}, Knud Jahnke, et al.
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, Universit√ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}

\begin{abstract}
We measure the relation between supermassive black hole and host galaxy properties at $1.2<z<1.7$ using a sample of 32 X-ray-selected broad-line (type-1) AGN in deep survey fields obtained with the Hubble Space Telescope (\hst) Wide-Field Camera 3. The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosity (\lhost) and stellar mass (\smass) in each case. Black holes masses (\mbh) are based on our published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines. We compare the \mbh-\lhost~and \mbh-\smass~relation to the local active galaxies while taking selection effects into account thus establishing the cosmic evolution in these relations. Results to be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. To be written. 
\end{abstract}

@@

In order to make progress it is important to reduced as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007,Lauer2007}. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones \citep{DeG++15}.

@@

\section{Sample selection}
%How the samples are selection.\\
%Where are they from?
%\\The redshift range? In a table?

@@

\section{HST observations}
\label{observation}
%\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection ensures that the broad \halpha\ line ($4000\AA$) is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.

@@

\section{Analysis}
\label{sec:analysis}

\subsection{Surface Photometry}
\subsubsection{PSF library}    
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be vary across the detector and with time, due to the effect of aberrations and breathing. Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}. Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}

@@

%\subsubsection{Surface Photometry modeling method}
\subsubsection{AGN-host Decomposition}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy. Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample. Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.

@@

\subsubsection{Host luminosity and stellar mass}
%The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
\textcolor{red}{To be written:}
\\1. Describe the SED fitting and the ground-based photometry data.
\\2. The comparison of our host-to-total flux ratios to the SED decomposed ones.
\\3. The inferred rest-frame R band magnitude and stellar mass.

@@

\section{Results}
\label{sec:result}
\subsection{\mbh-\lhost\ relation}

\subsection{\mbh-M$_*$ relation}
\subsubsection{Stellar mass estimates}
stellar mass \\

@@

\section{discuss}
\label{sec:dis}
\subsection{Systematic error}
\subsection{Masks objects for the COSMOS-CID206 and ECDFS-358}

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Inferred \mbh\.} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.992 & 5898.264 & 44.76243 & 8.833 \\
CID1281 & 1619.4891 & 43.23945 & 7.749 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.528 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.854 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.289 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.273 & 3709.241 & 45.37122 & 8.734 \\
CID3242 & 2543.2202 & 43.83323 & 8.449 & 3774.503 & 45.09891 & 8.613 \\
CID3570 & 1958.8551 & 43.16374 & 7.888 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.295 & 3127.3306 & 44.63353 & 8.217 \\
CID454 & 2824.2693 & 43.34466 & 8.311 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.423 & 1938.5676 & 45.32766 & 8.149 \\
CID543 & 2188.8447 & 43.57404 & 8.187 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.813 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.526 & 4241.526 & 44.78209 & 8.556 \\
CID70 & 2480.4058 & 43.50531 & 8.269 & 3981.8574 & 45.1582 & 8.689 \\
LID1273 & 3223.8484 & 43.61001 & 8.561 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.469 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.45 & 2868.8992 & 45.08676 & 8.369 \\
XID2138 & 3185.8613 & 43.6148 & 8.552 & 2944.7766 & 44.80782 & 8.252 \\
XID2202 & 2973.2378 & 43.56249 & 8.463 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
CDFS-1 & ... & ... & ... & ... & ... & ... \\
CDFS-229 & ... & ... & ... & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
CDFS-724 & ... & ... & ... & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & 6761.222 & 44.71429 & 8.927 \\
SXDS-X50 & 1816.672 & 43.421 & 7.942 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & 3519.6052 & 45.07463 & 8.54 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & 4508.5146 & 44.51285 & 8.474 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & 1695.7146 & 45.05337 & 7.895 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
}
\end{deluxetable*}

>>>>

\title{The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3}

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{2}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{2},  Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{2}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}

\begin{abstract}

The tight correlation between the mass of a supermassive black hole (\mbh) and its host galaxies properties indicates a connection of their evolution. The key to test this co-evolution scenario is to trace their correlation to more distant Universe. We measure using a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields obtained with the {\it Hubble Space Telescope} (\hst). %Wide-Field Camera 3.
The high-resolution \hst\ images enable us to decompose the AGN image and infer the host properties including luminosity (\lhost) and stellar mass (\smass) in each case. The lower nuclear-to-host ratios and multi-band images of our samples provide accurate host properties.
The estimation of \mbh\ is based on our published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids the systemic bias by the \Civ\ or \Mgii\ lines. We compare the \mbh-\lhost~and \mbh-\smass~relation to the local active galaxies while taking the selection effect into account thus establishing the cosmic evolution in these relations. Considering the passive luminosity effect, we inferred a positive evolution of \mbh-\lhost, indicating that the BHs at higher redshift resides in less luminous galaxies than today. The \mbh-\smass\ of our high redshift sample is consistent with the local \mbh-\smass$_{\rm bluge}$ relations. Considering that our sample are composed of bulge and disk components, we are forced to concluded that our results consistent to a scenario that the growth of the black hole predates that of the bulge.
\end{abstract}

@@

In order to make progress it is important to reduced as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called "virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-virial component of the BLR gas, when compared to local samples with masses based on broad Balmer lines \citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs \citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when intepreting the observations \citep{Treu2007, Lauer2007}. For instance, it has been demonstrated \citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones \citep{DeG++15}.

@@

\section{Sample selection and \mbh}
\label{sec:data}
%How the samples are selection.\\
%Where are they from?
%\\The redshift range? In a table?

@@

\section{\hst\ observations}
\label{observation}
%\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
The high spatial resolution of the host image is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. All the new 32 AGN systems were observed with the HST/WFC3 infrared channel, as the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection ensures that the broad \halpha\ line ($4000\AA$) is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.

@@

%\section{Analysis}
\subsection{PSF library}
\label{sec:psf_library}
%Introduce the PSF library
The knowledge of the PSF is crucial for the AGN imaging decomposition, especially when the nuclear image is unresolved with light distributed as the point source. The PSF is known to be vary across the detector and with time, due to the effect of aberrations and breathing. Simulated PSF, such as {\sc TinyTim} ones, are usually insufficient matches to observations for our purposes \citet{Mechtley2012}. Stars within the fields provide a better description than the simulated PSF, since they were observed simultaneously with the science targets and reduced and analyzed in the same way \citet{Kim2008, Park15}

@@

%\label{sec:analysis}

%\subsection{Surface Photometry}
%\subsubsection{PSF library}    
%\subsubsection{Surface Photometry modeling method}
\section{AGN-host Decomposition}
%Introduce the lenstronomy. Model the PSF in each library.\\
%Inspired by Simon's work, we rank the performance of the each PSF and weight for the final fitting result. 
We simultaneously fit the two-dimensional flux distribution of the center nuclear and the underlying host galaxy. Following common practice, we assume the unresolved nuclear as a scaled point source, while the host galaxy as a \sersic\ profile. Note that the actual morphologies of the host galaxies could be more complicated (e.g. bulge+disk). However, the purpose of adopting the \sersic\ model is a simplified a first-order approximation of the surface brightness distribution with a flexible parameterization which provides sufficient freedom to infer the host flux, given the high redshift range of our sample. Furthermore, we fit other galaxies that happen to be close to the AGN as additional \sersic\ model, to account for any potential contamination.

@@

\subsection{Masks objects for the COSMOS-CID206 and ECDFS-358}

\section{Results}
\label{sec:result}

\subsection{Host galaxy properties}
%The overall fitting plot: 1. Host-R-n corner for f140w and f814w. 2. The histogram with different selection.
\textcolor{red}{To be written:}
\\1. Describe the SED fitting and the ground-based photometry data.
\\2. The comparison of our host-to-total flux ratios to the SED decomposed ones.
\\3. The inferred rest-frame R band magnitude and stellar mass.

@@

\subsection{\mbh-\lhost\ relation}

\subsection{\mbh-M$_*$ relation}

\subsection{Selection effect}

\section{discussion}
\label{sec:dis}
\subsection{Systematic error}
\subsection{JWST}

@@

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Inferred \mbh\ .} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.992 & 5898.264 & 44.76243 & 8.833 \\
CID1281 & 1619.4891 & 43.23945 & 7.749 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.528 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.854 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.289 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.273 & 3709.241 & 45.37122 & 8.734 \\
CID3242 & 2543.2202 & 43.83323 & 8.449 & 3774.503 & 45.09891 & 8.613 \\
CID3570 & 1958.8551 & 43.16374 & 7.888 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.295 & 3127.3306 & 44.63353 & 8.217 \\
CID454 & 2824.2693 & 43.34466 & 8.311 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.423 & 1938.5676 & 45.32766 & 8.149 \\
CID543 & 2188.8447 & 43.57404 & 8.187 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.813 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.526 & 4241.526 & 44.78209 & 8.556 \\
CID70 & 2480.4058 & 43.50531 & 8.269 & 3981.8574 & 45.1582 & 8.689 \\
LID1273 & 3223.8484 & 43.61001 & 8.561 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.469 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.45 & 2868.8992 & 45.08676 & 8.369 \\
XID2138 & 3185.8613 & 43.6148 & 8.552 & 2944.7766 & 44.80782 & 8.252 \\
XID2202 & 2973.2378 & 43.56249 & 8.463 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.455 & 2657.8386 & 45.50467 & 8.511 \\
CDFS-1 & ... & ... & ... & ... & ... & ... \\
CDFS-229 & ... & ... & ... & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.457 & ... & ... & ... \\
CDFS-724 & ... & ... & ... & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 8.122 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.333 & 6761.222 & 44.71429 & 8.927 \\
SXDS-X50 & 1816.672 & 43.421 & 7.942 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 8.204 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.44 & 3519.6052 & 45.07463 & 8.54 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.465 & 4508.5146 & 44.51285 & 8.474 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.196 & 1695.7146 & 45.05337 & 7.895 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2-4: \halpha\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
Column 5-7: \hbeta\ emission line width (FWHM), continuum luminosity, and inferred \mbh. 
}
\end{deluxetable*}
